% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode

% In Class Activity for ME3001- Tristan Hill 
% Spring 2017 - Fall 2017 - Fall 2020 - Fall 2021
% Mechanical Engineering Analysis with MATLAB  and Solidworks
% Module 1 - Deisgn with Solidworks
% Activity 2 -(In-Class)- Introduction to Solidworks 

\documentclass[12pt]{article}
\usepackage{/home/thill/Documents/lectures/analysis_lectures/analysis_activities}

% Title and Misc
\newcommand{\COURNAME}{ME 3001-002}
\newcommand{\CURRTERM}{Fall 2021} %Current Term
\newcommand{\MNUM}{1} %Module Number
\newcommand{\ANUM}{2} %Activity Number
\newcommand{\moduletitle}{Deisgn with Solidworks}
\newcommand{\activitytitle}{Introduction to Solidworks} %Module Name
\pagestyle{myheadings}
%\markright{{\large ME4140 - ROS Workshop - \CURRTERM}}

\textwidth=7.0in
\topmargin=-0.6in
\leftmargin=0.5in
\textheight=9.25in
\hoffset=-0.5in
\footskip=0.2in

\begin{document}

\thispagestyle{plain}

\begin{center}
   {\bf \Large In-Class Activity\hspc\ANUM\hspc - \activitytitle}\vspace{3mm}\\
   {\bf \large \COURNAME - Mechanical Engineering Analysis - \CURRTERM} \vspace{5mm}\\
\end{center}

\begin{description}

\item[\textbf{\underline{Overview:}}] \hfill \vspace{3mm}\\
You will do some intital brainstorming and begin to draw you design in CAD.

\item[\textbf{\underline{Learning Objectives:}}] \hfill \vspace{0mm}

\begin{itemize}
	\item You will practice and learn to produce solid models in CAD to represent proposed design. 
\end{itemize}

\item[\textbf{\underline{Required Materials:}}] \hfill \vspace{0mm}

\begin{itemize}
	\item {\bf Your Computer}: This activity requires a computer with Solidworks installed.
\end{itemize}

\item[\textbf{\underline{Activity:}}] \hfill \vspace{0mm}

\begin{enumerate}
	

	\item Choose a device or machine to model for this project. It can be anything within reason, but it must meet the following criteria. Create an initial concept sketch of the system. If you are still deciding on a design or topic, include several concept sketches. 
	
	\item After choosing the main concepts for the part. Choose reasonable variable names for the primary dimensions and add these to at least on sketch of the system. Include the concept sketches from part 1 and part 2 in a file {\bf \BL<USERNAME>\BK\_part1.pdf}. 
	
	\item Create a 3D model using solidworks of a single part or component of the system. This part should be saved as a {\bf \BL<USERNAME>\BK\_part1.sldprt}. 
	
	\item {\it If time allows}, save the part and make revisions for improvement. Altenatively, begin in working on the design of the remaing 
\end{enumerate}

\item[\textbf{\underline{Submit:}}] \hfill \vspace{0mm}

		Submit the most complete version of {\bf \BL<USERNAME>\BK\_part1.sldprt} \\and {\bf \BL<USERNAME>\BK\_part1.pdf } to the Activity \ANUM \hspace{1mm} folder before the posted due date.

\end{description}
\end{document}
