\documentclass[12pt]{article}
\usepackage{hyperref}
\usepackage[pdftex]{graphicx}
\usepackage{multirow}
\usepackage{setspace}
\usepackage{color}
\usepackage{multicol}
\usepackage{framed}


% ME3001 - spring 2017 - Fall 2017 - Fall 2019
% Tristan Hill - naming convention

\textwidth=6.5in
\topmargin=-0.5in
\textheight=9.25in
\hoffset=-0.5in
\footskip=0.2in

\pagestyle{myheadings}
\markright{{\large ME 3001 -- Homework Format for Digital Submission}}

\newcommand{\VSIZE}{2mm}

\begin{document}

%\thispagestyle{plain}
    
	{\bf !!! FOLLOW THESE INSTRUCTIONS TO RECEIVE CREDIT !!!}\\\\
    You will be submitting all of your code using the {\it assignments} feature in {\it ilearn}. The due dates for all assignments are posted but those dates are subject to change. Assignments will not be submitted through email. You will not receive credit if you email me your code. \\
    
    \begin{itemize}
    
	\item {\bf \underline{ Assignment Summary Document}:} \vspace{2mm} \\  
Each homework submission will include a document that describes the core elements of the assignment. You can generate the document using the software of your choice but it must be submitted in .pdf file format. All text must be typed and I encourage you to type or import any equations or data used. The following elements are required in the summary document.\\
	\begin{itemize}
	\item{\bf Problem Statement:} This information is provided by the instructor. You can import the .pdf or copy the text into your summary document. \\
	\item {\bf Mathematical Modeling:}  A description the governing mathematical models, equations, and/or important assumptions is required. This may vary by assignment. \\
	\item {\bf Figures and/or Schematics:}  Any figures, diagrams, or schematics showing the important details problem should be included. These may be provided by the instructor or generated by the students. \\

	\item {\bf Solution and Analysis:}  All calculations and methods used to complete the assignment will submitted and thoroughly documented. If any of these items does not cleanly fit in to the document they should be included as a separate file but they must referenced in this section of the summary document.   
\begin{itemize}
	\item hand calculations (must be readable)
	\item MATLAB scripts and outputs (must be clean* and readable)
	\item algorithms implemented
\end{itemize}
 
	\item {\bf Results and/or Conclusions:} The quantitative and qualitative results must be provided along with a brief discussion. This includes any numerical answers as well a description of their significance and feasibility. 
	
	{\bf    All significant results and answers to numbered questions must be present in the summary document. Results that are only present in the analysis code or files may not be reviewed by the grader. } \\
	
	

	\end{itemize}
	

\item {\bf Analysis and Data Files:} \vspace{2mm} \\  
Any additional files used for the assignment or referenced in the summary must be included in the submission. These may include but are not limited to the following file types. All MATLAB scripts must be submitted as .m files.

\newpage


	\item {\bf Grading Rubric:} \vspace{2mm} \\  
Assignment grades will be based on the grading rubric associated the assignment in ilearn. Each assignment will be based off a standard template but may have specific details. \\

    	\item {\bf Submit All Files Separately:} \vspace{2mm} \\  
All files for a single assignment must be submitted separately. DO NOT submit them as a compressed file such as .zip or .tar.gz . If you have questions please ask the instructor or a peer. \\
 
   	\item {\bf Use the Reasonable File Names:}\vspace{2mm} \\
Specific instructions may be given on each assignment describing the required filenames. If the filenames are not given or you want to add additional files, you are free to choose your own file names. Choose reasonable and descriptive filenames because the instructor must review the files. \\

 

%\begin{itemize}
%       \item {\bf Groups of 2} \\ \vspace{2mm}
%        example:\\ John Robert Smith ({\bf jrsmith42}@students.tntech) is in a group with \\\\ Jane Sue Doe ({\bf jsdoe21}@students.tntech),
%        they {\it must} name the {\it .zip} file: 
%        \begin{framed}
%        {\fontfamily{qcr}\selectfont
%        { jrsmith42\textunderscore jsdoe21\textunderscore hw1.zip}    
%        }\end{framed}
%   
%        \item  {\bf Individuals:}\\ 
%        example:\\ Tristan William Hill ({\bf twhill21}@students.tntech) {\it must} name the {\it .zip} file:
%        \begin{framed}
%        {\fontfamily{qcr}\selectfont
%        {twhill21\textunderscore hw1.zip}               
%        }\end{framed}
%        \vspace{5mm}
%        
%    \end{itemize}
        
%        \item {\bf Groups of 3} \\ \vspace{2mm}
%        example:\\ John Robert Smith ({\bf jrsmith42}@students.tntech) is in a group with \\\\ Jane Sue Doe ({\bf jsdoe21}@students.tntech) and `The Boz' ({\bf bsbosworth21}@students.tntech)
%        they {\it must} name the {\it .zip} file: 
%        \begin{framed}
%        {\fontfamily{qcr}\selectfont
%        { jrsmith42\textunderscore jsdoe21\textunderscore bsbosworth21\textunderscore hw1.zip}    
%        }\end{framed}
        
       
        %\vspace{5mm}
      
     
        \item {\bf iLearn Submission:}\\ \\
There will be an {\it assignments} folder for each assignment that requires digital submission on the {\it ilearn} website. If you would like to re-submit a correction of updated file, please wait at least 2 minutes between submissions. Only the most recently submitted file will be graded.
   
   	\item {\bf Group Assignments:} \vspace{2mm} 
   \\
   Some homework assignments, designated as Group Assignments in ilearn, may be completed in homework groups of up to two students. Only one submission is required per group, and it can come from any member of the group. Include all group member names on any documents or work that was completed by the group.         
           
            
        
    \end{itemize}

    


\end{document}

