\documentclass[12pt]{article}
\usepackage{hyperref}
\usepackage[pdftex]{graphicx}
\usepackage{multirow}
\usepackage{setspace}
\usepackage{color}
\usepackage{multicol}
\usepackage{framed}


% ME3001 - spring 2017 - Fall 2017
% Tristan Hill - naming convention

\textwidth=6.5in
\topmargin=-0.5in
\textheight=9.25in
\hoffset=-0.5in
\footskip=0.2in

\pagestyle{myheadings}
\markright{{\large ME 3001---Digital Submission Naming Convention}}

\newcommand{\VSIZE}{2mm}

\begin{document}

%\thispagestyle{plain}
    
	{\bf !!!!! YOU MUST FOLLOW THIS TO RECIEVE CREDIT !!!!!}\\\\
    You will be submitting all of your code using the {\it assignments} feature in {\it ilearn}. The due dates for all assignments are posted but those dates are subject to change. Assignments will not be submitted through email. You will not receive credit if you email me your code. \\
    
    \begin{itemize}
    
    	\item {\bf Compressed Folder:}\\
Most assignments will require more than 1 file to complete. All files for a single assignment will be compressed into a {\it .zip} file (compressed folder). You must do this even if there is a just 1 file. If you need help please let me know or ask a peer. 
    
        \item  {\bf Individuals:}\\ 
        example:\\ Tristan William Hill ({\bf twhill21}@students.tntech) {\it must} name the {\it .zip} file:
        \begin{framed}
        {\fontfamily{qcr}\selectfont
        {twhill21\textunderscore hw1.zip}               
        }\end{framed}
        %\vspace{5mm}
        
        \item {\bf Groups of 2} \\ \vspace{2mm}
        example:\\ John Robert Smith ({\bf jrsmith42}@students.tntech) is in a group with \\\\ Jane Sue Doe ({\bf jsdoe21}@students.tntech),
        they {\it must} name the {\it .zip} file: 
        \begin{framed}
        {\fontfamily{qcr}\selectfont
        { jrsmith42\textunderscore jsdoe21\textunderscore hw1.zip}    
        }\end{framed}
        
        \item {\bf Groups of 3} \\ \vspace{2mm}
        example:\\ John Robert Smith ({\bf jrsmith42}@students.tntech) is in a group with \\\\ Jane Sue Doe ({\bf jsdoe21}@students.tntech) and `The Boz' ({\bf bsbosworth21}@students.tntech)
        they {\it must} name the {\it .zip} file: 
        \begin{framed}
        {\fontfamily{qcr}\selectfont
        { jrsmith42\textunderscore jsdoe21\textunderscore bsbosworth21\textunderscore hw1.zip}    
        }\end{framed}
        
       
        %\vspace{5mm}
      
     
        \item {\bf Submission} There will be an {\it assignments} folder for each assignment that requires digital submission on the {\it ilearn} website. Only 1 submission per group is required. However if you would like to re-submit a correction, you may do so, but please wait at least 2 minutes between submissions. Only the most recently submitted file will be graded.
            
        
    \end{itemize}

    


\end{document}

