% Lecture Template for ME3001-001-Tristan Hill - Spring 2017 - Fall 2018
% 
% Mechanical Engineering Analysis with MATLAB
%
% Exam  Review - ME3001 - Spring 2020


% Document settings
\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[pdftex]{graphicx}
\usepackage{multirow}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{color,soul}
\usepackage{fancyvrb}
\usepackage{framed}
\usepackage{wasysym}
\usepackage{multicol}

\pagestyle{plain}
\setlength\parindent{0pt}
\hypersetup{
    bookmarks=true,         % show bookmarks bar?
    unicode=false,          % non-Latin characters in Acrobat’s bookmarks
    pdftoolbar=true,        % show Acrobat’s toolbar?
    pdfmenubar=true,        % show Acrobat’s menu?
    pdffitwindow=false,     % window fit to page when opened
    pdfstartview={FitH},    % fits the width of the page to the window
    pdftitle={My title},    % title
    pdfauthor={Author},     % author
    pdfsubject={Subject},   % subject of the document
    pdfcreator={Creator},   % creator of the document
    pdfproducer={Producer}, % producer of the document
    pdfkeywords={keyword1} {key2} {key3}, % list of keywords
    pdfnewwindow=true,      % links in new window
    colorlinks=true,       % false: boxed links; true: colored links
    linkcolor=red,          % color of internal links (change box color with linkbordercolor)
    citecolor=green,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=blue           % color of external links
}

% assignment number 

\definecolor{mygreen}{rgb}{0, .39, 0}

%\definecolor{dred}{#8B0000}
% [153,50,204] - dark orchid
\definecolor{mypurple}{rgb}{0.6,0.1961,0.8}
%[139,69,19] - saddle brown
\definecolor{mybrown}{rgb}{0.5451,0.2706,0.0745}

\definecolor{mygray}{rgb}{.6, .6, .6}

\setulcolor{red} 
\setstcolor{green} 
\sethlcolor{mygray} 

\newcommand{\VA}{\vspace{2mm}}
\newcommand{\VB}{\vspace{5mm}} 
\newcommand{\VC}{\vspace{30mm}} 
 
\newcommand{\R}{\color{red}}
\newcommand{\B}{\color{blue}}
\newcommand{\K}{\color{black}}
\newcommand{\G}{\color{mygreen}}
\newcommand{\PR}{\color{mypurple}}

\newcommand{\NUM}{1} 
\newcommand{\VSpaceSize}{2mm} 
\newcommand{\HSpaceSize}{2mm} 

\begin{document}

\textbf{ \LARGE ME3001 - 002 - Spring 2020 - Exam 2 Review  } \\\\

\large
\begin{itemize}
	\item  \textbf{\Large General Information}\\

	\begin{itemize}

		\item  \textbf{Date: Friday 04/24/2020 }\\
		\item  \textbf{\underline{Start Time}: 12:20 AM\hspace{5mm}\underline{Stop Time}: 2:20 PM}\\
		\item  \textbf{Location: The exam will be taken remotely. }\\
		\item  \textbf{Access the exam at Start Time on ilearn.} \\
		\item  \textbf{Submit your work as a .pdf before Stop Time on ilearn.}\\ 
		\item  \textbf{Label all answers. \underline{Do not} write the problem statements.}\\
	\end{itemize}

		\item  \textbf{\Large Materials Allowed in Exam}\\

	\begin{itemize}

		\item  \textbf{Calculator of your Choice (i.e. TI, MATLAB, abacus)}\\
		\item  \textbf{Your notes from class}\\
		\item  \textbf{Reference Sheet(s) from Instructor}\\
		\item  \textbf{A writing device of your choice, pencil or tablet}\\
		\item  \textbf{You are not allowed to use external resources such as the \\internet or communicate with anyone besides the instructor during test}\\

		\item \textbf{ This is a Self Proctored Exam - You are responsible for upholding the TNTECH Student Academic Misconduct Policy. You must write, sign and date the following honesty contract on the first page of your exam. }\\
\end{itemize}
\large 
		\item \textbf{Honesty Contract:}
\begin{framed}
		 \textbf{I \underline{\hspace{50mm}}, agree to follow the policy of this exam as described in the document {\it me3001\_exam2\_honestycontract.pdf. }}\vspace{3mm}\\
		 \textbf{Signature\underline{\hspace{80mm}}\hspace{10mm}Date\underline{\hspace{20mm}}}\\
\end{framed}
	
\newpage
\item  \textbf{\Large Topics Covered}\\
	\begin{itemize}

		\item  \textbf{\large Classification of Differential Equations}\vspace{0mm}\\
		\item  \textbf{\large Analytical Solutions to ODEs}\vspace{0mm}\\
		\item  \textbf{\large Numerical Soltions to ODEs}\vspace{0mm}\\
		\item  \textbf{\large Equation Decomposition}\\


	\end{itemize}

\item  \textbf{\Large Probable Problem Breakdown}\\
\Large
	\begin{enumerate}


		\item  \textbf{\Large Technical Problem A (33.33\%)}\\
		\begin{itemize}
			\item No Model - Just Math
			\item Solve ODE $1^{st}$\hspace{3mm} $2^{nd}$
			\item Separation of Variables or The Trial Solution Method\\
		\end{itemize}
		\item  \textbf{\Large Technical Problem B (33.33\%)}\\
		\begin{itemize}
		
			\item Analytical Solution 
			\item Numerical Integration for Solution Validation 
			\item Sketch of Solutions \\

		\end{itemize}
		\item  \textbf{\Large Technical Problem C (33.33\%)}\\
		\begin{itemize}
			\item Given mathematical model 
			\item Numerical Integration	for Solution 
			\item Decomposition of Second Order Equation
			\item Analyis question


		\end{itemize}
	\end{enumerate}
%
%\item  \textbf{\Large Solutions from TH}\\
%\begin{itemize}
%\item QZ 3,4,5
%\item HW 3,4
%\end{itemize}

\end{itemize}


	

\end{document}



