% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode

% In Class Activity for ME3001- Tristan Hill 
% Spring 2017 - Fall 2017 - Fall 2020 - Fall 2021
% Mechanical Engineering Analysis with MATLAB  and Solidworks
% Module 1 - Deisgn with Solidworks
% Activity 7 -(In-Class)- Solidworks Assemblies

\documentclass[12pt]{article}
\usepackage{/home/thill/Documents/lectures/analysis_lectures/analysis_activities}

% Title and Misc
\newcommand{\COURNAME}{ME 3001-002}
\newcommand{\CURRTERM}{Fall 2021} %Current Term
\newcommand{\MNUM}{1} %Module Number
\newcommand{\ANUM}{7} %Activity Number
\newcommand{\moduletitle}{Deisgn with Solidworks}
\newcommand{\activitytitle}{Solidworks Assemblies} %Module Name
\pagestyle{myheadings}
%\markright{{\large ME4140 - ROS Workshop - \CURRTERM}}

\textwidth=7.0in
\topmargin=-0.6in
\leftmargin=0.5in
\textheight=9.25in
\hoffset=-0.5in
\footskip=0.2in

\begin{document}

\thispagestyle{plain}

\begin{center}
   {\bf \Large In-Class Activity\hspc\ANUM\hspc - \activitytitle}\vspace{3mm}\\
   {\bf \large \COURNAME - Mechanical Engineering Analysis - \CURRTERM} \vspace{5mm}\\
\end{center}

\begin{description}

\item[\textbf{\underline{Overview:}}] \hfill \vspace{3mm}\\
You will develop your Solidworks mini-project design in CAD and begin to construct a Solidworks assembly.

\item[\textbf{\underline{Learning Objectives:}}] \hfill \vspace{0mm}

\begin{itemize}
	\item Practice creating fully-defining 2D sketches.  
	\item Practice using extrude and revolve to create 3D features.
	\item Learn to produce assemblies from multiple part files.
	 
\end{itemize}

\item[\textbf{\underline{Required Materials:}}] \hfill \vspace{0mm}

\begin{itemize}
	\item {\bf Computer}: This activity requires a computer with Solidworks installed.
\end{itemize}

\item[\textbf{\underline{Activity:}}] \hfill \vspace{0mm}

\begin{enumerate}
	

	\item Choose at least two different parts from your mini design project. Create a representative part model for each piece in Solidworks and save the part file as {\bf \BL<USERNAME>\BK\_partA.sldprt} and {\bf \BL<USERNAME>\BK\_partB.sldprt}. Additional parts may be included. 
	 \
	
	\item Create a Solidworks assembly from the individual parts. Click {\it New -> Assembly} to open a new assembly and save the file as {\bf \BL<USERNAME>\BK\_assemblyAB.sldasm}. 
	\item {\it If time allows}, save a copy of your work and begin to make revisions for improvement. Alternatively, begin working on the design of the remaining components of the project. 
\end{enumerate}

\item[\textbf{\underline{Submit:}}] \hfill \vspace{0mm}

		Submit the most complete version of the following files to the Activity \ANUM \hspace{1mm} ilearn folder before the posted due date. Additional parts may be included.
		\begin{itemize}
			\item {\bf \BL<USERNAME>\BK\_partA.sldprt}
			\item {\bf \BL<USERNAME>\BK\_partB.sldprt}
			\item {\bf \BL<USERNAME>\BK\_assemblyAB.sldasm}
			
		\end{itemize}  

\end{description}
\end{document}
